
## Data 605 - Assignment 10

**Hazal Gunduz**

**Exercise:** Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars. A guard agrees to make a series of bets with him. If Smith bets A dollars, he wins A dollars with probability .4 and loses A dollars with probability .6.

Find the probability that he wins 8 dollars before losing all of his money if

(a) he bets 1 dollar each time (timid strategy).

(b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy).

(c) Which strategy gives Smith the better chance of getting out of jail?

**(a) (timid strategy)**

```{r}
p <- 0.4
q <- 0.6
r <- q / p

A <- (1 - (q / p)^1) / (1 - (q / p)^8)
A
```

**The probability that he wins 8 dollars before losing all of his money if (a) he bets 1 dollar each time (timid strategy) is 0.0203**

**(b) (bold strategy)**

**Since Smith tries to double his money each time, he can't reach every integer before 8. It can go from 1 to 0 or 2. It can go from 2 to 4 or 0. Finally it can go from 4 to 8 or 0.**

```{r}
B <- dbinom(3, 3, p)
B
```

**The probability that he wins 8 dollars before losing all of his money if (b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy) is 0.064**

**(c) (better strategy)**

**Comparing the probabilities of  strategies, the bold strategy of "0.064" gives to Smith a better and higher chance than the timid strategy of "0.0203".**

Rpubs => https://rpubs.com/gunduzhazal/1023509

